The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
who gives an eff about an oxford comma

<!-- Figure 3: metrics by social scale -->
(ref:socres) Varying scale in social threshold. For each social threshold, multilayer
networks were constructed for each landcover class (forest, lichen and open)
across two seasons (summer and winter) and four network metrics calculated.  A)
Mean graph strength across individuals showed an increase for winter network
layers at 50 m through 500 m while summer network layers had consistently weak
connections. B) Mean layer relevance was relatively stable across social
thresholds for each season and landcover layer. C) Similarity of landcover
network layers between seasons (e.g. open summer compared to open winter)
showed different responses to changing landcover scale with an overall increase
in similarity for open layers and decrease in similarity for lichen layers.
<!--TODO: what about forest.--> D) Mean connective redundancy across individuals
increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at
approximately a 50 m <!--TODO:**??**--> social threshold before decreasing
between 400 m and 500 m.

@@

<!-- Figure 4: metrics by landcover resolution -->
(ref:lcres) Variation in multilayer network metrics as a function of changes in
landcover resolution, a metric which we interpret as spatial scale. For each
landcover resolution, multilayer networks were constructed for each landcover
class (forest, lichen and open) across two seasons (summer and winter), and four
network metrics were calculated and we examined how network metrics changed as a
function of changes in spatial scale. A) Mean graph strength of individuals was
weaker during the summer compared to the winter months. B) Mean layer relevance
showed sparse connectivity in summer compared to winter networks and a decrease
in winter lichen layer relevance at higher landcover resolutions. C) Similarity
of landcover network layers between seasons (e.g. open summer compared to open
winter) showed different responses to changing landcover scale with an increase
in similarity for forest layers at 250 m and decrease in similarity for open
layers at 250 m. Note that lichen layer similarity is not shown because
individuals did not interact in lichen habitats greater greater than 10 m
landcover resolution. D) Mean connective redundancy across individuals showed a
decreasing trend with increasing landcover resolution.

@@

<!-- Figure 5: metrics by number of observations -->
<!-- TODO: RO first sentence... -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number
of observations (10-485 observations in steps of 25) were selected from the
complete data set to construct multilayer networks with layers defined by each
landcover class (forest, lichen and open) across two seasons (summer and winter)
and four network metrics calculated. A) Mean graph strength across individuals
varied for winter layers becoming relatively stable at 200 observations and
remained weak throughout for summer layers. B) Mean layer relevance across
individuals increased for winter layers and slightly increased for summer
layers. C) Similarity of landcover network layers between seasons (e.g. open
summer compared to open winter) showed a stabilizing layer similarity at 200
observations for forest and 300 observations for lichen and open.
<!--TODO:*There were observations of individuals in lichen and open areas at
lower numbers of observations during the winter, so layer similarity could not
be calculated at these values.* **Brief explanation of why two landcover don't
have values at lower nobs??**.--> D) Mean connective redundancy across
individuals increased with increasing number of observations, which begins to
plateau around 100 observations.

>>>>

<!-- Figure 3: metrics by social scale -->
(ref:socres) Varying scale in social threshold. For each social threshold, multilayer
networks were constructed for each landcover class (forest, forage, and open)
across two seasons (summer and winter) and four network metrics calculated.  A)
Mean graph strength across individuals showed an increase for winter network
layers at 50 m through 500 m while summer network layers had consistently weak
connections. B) Mean layer relevance was relatively stable across social
thresholds for each season and landcover layer. C) Similarity of landcover
network layers between seasons (e.g. open summer compared to open winter)
showed different responses to changing landcover scale with an overall increase
in similarity for open layers and decrease in similarity for lichen layers.
<!--TODO: what about forest.--> D) Mean connective redundancy across individuals
increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at
approximately a 50 m <!--TODO:**??**--> social threshold before decreasing
between 400 m and 500 m.

@@

<!-- Figure 4: metrics by landcover resolution -->
(ref:lcres) Variation in multilayer network metrics as a function of changes in
landcover resolution, a metric which we interpret as spatial scale. For each
landcover resolution, multilayer networks were constructed for each landcover
class (forest, forage, and open) across two seasons (summer and winter), and four
network metrics were calculated and we examined how network metrics changed as a
function of changes in spatial scale. A) Mean graph strength of individuals was
weaker during the summer compared to the winter months. B) Mean layer relevance
showed sparse connectivity in summer compared to winter networks and a decrease
in winter lichen layer relevance at higher landcover resolutions. C) Similarity
of landcover network layers between seasons (e.g. open summer compared to open
winter) showed different responses to changing landcover scale with an increase
in similarity for forest layers at 250 m and decrease in similarity for open
layers at 250 m. Note that lichen layer similarity is not shown because
individuals did not interact in lichen habitats greater greater than 10 m
landcover resolution. D) Mean connective redundancy across individuals showed a
decreasing trend with increasing landcover resolution.

@@

<!-- Figure 5: metrics by number of observations -->
<!-- TODO: RO first sentence... -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number
of observations (10-485 observations in steps of 25) were selected from the
complete data set to construct multilayer networks with layers defined by each
landcover class (forest, forage, and open) across two seasons (summer and winter)
and four network metrics calculated. A) Mean graph strength across individuals
varied for winter layers becoming relatively stable at 200 observations and
remained weak throughout for summer layers. B) Mean layer relevance across
individuals increased for winter layers and slightly increased for summer
layers. C) Similarity of landcover network layers between seasons (e.g. open
summer compared to open winter) showed a stabilizing layer similarity at 200
observations for forest and 300 observations for lichen and open. 
<!--TODO:*There were observations of individuals in lichen and open areas at
lower numbers of observations during the winter, so layer similarity could not
be calculated at these values.* **Brief explanation of why two landcover don't
have values at lower nobs??**.--> D) Mean connective redundancy across
individuals increased with increasing number of observations, which begins to
plateau around 100 observations. Note, data in panel C are truncated because 
there were observations of individuals in lichen and open areas at
lower numbers of observations during the winter, so layer similarity could not
be calculated at these values.
